Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-07-20 manuscript/supplement_motifs.tex

>>>>

    \begin{figure}[h!]
        \centering
        \includegraphics[height=0.75\textheight]{figures/persistence_vs_BSC_lm.eps}
        \caption{Persistence decreased strongly with increasing probability of disturbance to basal resources, while the proportion of the network made up of basal resources, network size, connectance, and their interactions had smaller effects. We show relationships with persistence for low disturbance ($\pi_{Basal}$=0.1) and high disturbance($\pi_{Basal}$=0.5). For each predictor other than disturbance, we show the relationship between the focal predictor and persistence for combinations of the lowest and highest observed values of the other predictors. For proportion of basal resources, these values were 0.02 and 0.5; for network size, 50 and 100; and for connectance, 0.02 and 0.18.}
        \label{fig:lm_BCS}
    \end{figure}
